A Mechanical Formalization of Higher-Ranked Polymorphic Type Inference

### 2019-02-28 sections/Metatheory.tex
minor typos

\begin{figure}
\centering\begin{tabular}{|c|c|c|l|}\hline
    File(s) & SLOC & \#Theorems & Description\\\hline
    olist.thm, nat.thm  &  309 & 56  & Basic data structures\\\hline
    typing.thm          &  238 & 5   & Declarative \& algorithmic system, debug examples\\\hline
    decl.thm            &  226 & 33  & Basic declarative properties\\\hline
    order.thm           &  235 & 27  & The $|\cdot|_\forall$ measure; decl. subtyping strenthening\\\hline
    alg.thm             &  655 & 72  & Basic algorithmic properties\\\hline
    trans.thm           &  628 & 53  & \makecell[l]{Transfer and its basic properties \\
                            Lemmas~\ref{lem:insert}, \ref{lem:extract}}\\\hline
    declTyping.thm      &  944 & 72  & \makecell[l]{Additional properties for declarative typing \\
                            Lemmas~\ref{lem:inv_allR}, \ref{lem:inv_chkAll}, \ref{lem:inv_chkLam}}\\\hline
    soundness.thm       & 1069 & 70  & Soundness theorem; aux. lemmas on transfer\\\hline
    depth.thm           &  206 & 14  & \makecell[l]{The $|\cdot|_\to$ measure; \\
                            Lemma~\ref{lem:prune_inst}}\\\hline
    \makecell{dcl.thm, \\completeness.thm} & 1458 & 73  &
                            Completeness theorem; aux. lemmas and relations\\\hline
    inst\_decidable.thm &  830 & 42  & Lemma~\ref{lemma:inst:decidable} Instantiation Decidability\\\hline
    decidability.thm    &  885 & 50  & Lemma~\ref{lemma:inst:decidable}\\\hline
    Total               & 7683 & 567 & (51 definitions in total)\\\hline
\end{tabular}
\caption{Statistics for the proof scripts}
\label{fig:proof_statistics}
\end{figure}

>>>>

\begin{figure}[ht]
\centering\begin{tabular}{|c|c|c|l|}\hline
    File(s) & SLOC & \#Theorems & Description\\\hline
    olist.thm, nat.thm  &  309 & 56  & Basic data structures\\\hline
    typing.thm          &  238 & 5   & Declarative \& algorithmic system, debug examples\\\hline
    decl.thm            &  226 & 33  & Basic declarative properties\\\hline
    order.thm           &  235 & 27  & The $|\cdot|_\forall$ measure; decl. subtyping strenthening\\\hline
    alg.thm             &  655 & 72  & Basic algorithmic properties\\\hline
    trans.thm           &  628 & 53  & \makecell[l]{Transfer and its basic properties \\
                            Lemmas~\ref{lem:insert}, \ref{lem:extract}}\\\hline
    declTyping.thm      &  944 & 72  & \makecell[l]{Additional properties for declarative typing \\
                            Lemmas~\ref{lem:inv_allR}, \ref{lem:inv_chkAll}, \ref{lem:inv_chkLam}}\\\hline
    soundness.thm       & 1069 & 70  & Soundness theorem; aux. lemmas on transfer\\\hline
    depth.thm           &  206 & 14  & \makecell[l]{The $|\cdot|_\to$ measure; \\
                            Lemma~\ref{lem:prune_inst}}\\\hline
    \makecell{dcl.thm, \\completeness.thm} & 1458 & 73  &
                            Completeness theorem; aux. lemmas and relations\\\hline
    inst\_decidable.thm &  830 & 42  & Lemma~\ref{lemma:inst:decidable}\\\hline
    decidability.thm    &  885 & 50  & Decidability theorem\\\hline
    Total               & 7683 & 567 & (51 definitions in total)\\\hline
\end{tabular}
\caption{Statistics for the proof scripts}
\label{fig:proof_statistics}
\end{figure}
